### 2020-04-29 final_report/results.tex
revise second experiment

The results of the second experiment, shown in~\cref{fig:exp2-time-vs-reg},
seem to confirm our expectations. Compared to the previous experiment, we observe
that many surrogate families consistently achieved worse regression
performance and prediction times in a more complex, unrestricted domain. The least
affected models appear to be gradient boosted trees, artificial neural networks and extremely
randomised trees, which are known to be capable of capturing relationships
involving mixed feature types that were deliberately withheld in the first
experiment. With only negligible differences, the first two of these families
appear to be tied for the best performance as well as the shortest prediction
time. While extremely randomised trees and radial basis functions also
demonstrated satisfactory properties, other families failed to achieve
comparable regression performance, and in some cases also prediction time.

>>>>

The results of the second experiment, shown in~\cref{fig:exp2-time-vs-reg},
seem to confirm our expectations. Compared to the previous case, we observe
that many surrogate families consistently achieved worse regression
performance and prediction times in a more complex, unrestricted domain. The least
affected models appear to be gradient boosted trees, artificial neural networks and extremely
randomised trees, which are known to be capable of capturing relationships
involving mixed feature types that were deliberately withheld in the first
experiment. With only negligible differences, the first two of these families
appear to be tied for the best performance as well as the shortest prediction
time. We observe that extremely randomised trees and radial basis functions also
demonstrated satisfactory results, outperforming the remaining surrogates in
terms of regression performance, and in some cases also in prediction time.
